### 2019-08-01 reports/thesis/chapters/2_dataCollection.tex
data collection chpater contains black white images

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction}
  \label{fig:data_shadingCorrectionExample_image}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
      \caption{Black - BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
      \caption{Black - Linear shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
      \caption{White - BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
      \caption{White - Linear shading correction}
    \end{subfigure}
  }
  \caption{The black and white images after shading correction from the \texttt{AbsNoFilter} dataset.}
  \label{fig:data_shadingCorrectionExample_greyscale}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}

>>>>

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction.}
  \label{fig:data_shadingCorrectionExample_image}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_null.eps}
      \caption{Black - No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_null.eps}
      \caption{White - No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
      \caption{Black - BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
      \caption{White - BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
      \caption{Black - Linear shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
      \caption{White - Linear shading correction}
    \end{subfigure}
  }
  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset.}
  \label{fig:data_shadingCorrectionExample_greyscale}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The box plots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}
